Psychological Needs During Intergroup Contact

### 2021-11-04 Methods-and-Results.Rmd
linesep added

```{r workerVarDescr, include=FALSE}
workerMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
  )

@@

```{r workerOutVarDescr, include=FALSE}
workerOutMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
  )

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

@@

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

medicalOutMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  landscape() %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/medicalOutVarDescr.tex")

>>>>

```{r workerVarDescr, include=FALSE}
workerMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
  )

@@

```{r workerOutVarDescr, include=FALSE}
workerOutMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
  )

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

@@

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
  )

medicalOutMlCor %>%
  kable(
    .,
    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
    format = "latex",
    booktabs = TRUE,
    linesep = linesep(c(ncol(.))),
    align = c("l", rep("c", ncol(.) - 1))
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person coorelations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kableExtra::landscape() %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/medicalOutVarDescr.tex")
